working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
edits

[add table with morphometrical traits to appendix]()

@@

Mantel test indicates that a possible?? [It exists!]() correlation exist between heterospecific pollen effect and the evolutive relative distances, for ITS and RBCL markers we had r coefficients of 0.29 and 0.25 respectively p<0.05 [think on a figure - maybe using NMDS](). Moreover, Mantel test indicates that also a possible?? correlation between stigma width and stigma type exist (stats??). Trait correlations were also explored with GLMM

[I have done it at the moment just for Compatibility system](Jose)
[Also I have to fix from mixed linear model to GLMM, just realize that](Jose)

@@

Open with the main results...

>>>>

[explain ratios and total pollen](Jose)
[add table with morphometrical traits to appendix]()

@@

@@

Interestingly the effect of the different donors per species were very homogeneous which lead us to think that the female reproductive traits of the pollen recipient are the main ones in explaining heterospecific pollen effect. Our main predictive trait of effect is stigma size, and because we found a correlation between the pollen quantity deposited on the stigma and stigma size, we argue that that the total load of pollen deposited per treatment can obscured what are the main traits in driving heterospecific pollen effect.

Curiously between the species with greater effect sizes, we found completely self incompatible species, species with the smallest stigma and the species with shortes style. Develop more...

### 2019-03-13 Manuscript_draft/Manuscript_draft.tex
adding effect size of phylo to draft
edits

@@

Mantel test indicates that a possible?? \href{}{It exists!} correlation
exist between heterospecific pollen effect and the evolutive relative
distances, for ITS and RBCL markers we had r coefficients of 0.29 and
0.25 respectively p\textless{}0.05 \href{}{think on a figure - maybe
using NMDS}. Moreover, Mantel test indicates that also a possible??
correlation between stigma width and stigma type exist (stats??). Trait
correlations were also explored with GLMM

\href{Jose}{I have done it at the moment just for Compatibility system}
\href{Jose}{Also I have to fix from mixed linear model to GLMM, just
realize that}

@@

Open with the main results\ldots{}

>>>>

\href{Jose}{explain ratios and total pollen} \href{}{add table with
morphometrical traits to appendix}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
\caption{Phylogenetic signal of the average heterospecific pollen effect
size per species}
\end{figure}

@@

Interestingly the effect of the different donors per species were very
homogeneous which lead us to think that the female reproductive traits
of the pollen recipient are the main ones in explaining heterospecific
pollen effect. Our main predictive trait of effect is stigma size, and
because we found a correlation between the pollen quantity deposited on
the stigma and stigma size, we argue that that the total load of pollen
deposited per treatment can obscured what are the main traits in driving
heterospecific pollen effect.

Curiously between the species with greater effect sizes, we found
completely self incompatible species, species with the smallest stigma
and the species with shortes style. Develop more\ldots{}
